Dynamic parameter estimation in the nested multinomial logit choice model

### 2021-08-10 paper/paper.tex
rev

\subsection{Why the parameter update converges}
Consider the multivariate root-finding problem \[\text{find } \theta^*: F(\theta^*) = 0\]
and the iterative scheme \[\theta^{(t+1)} = \theta^{(t)} + \frac{\alpha}{t^r} F\left(\theta^{(t)} \right)\]
where $\alpha >0$ and $r \in (0, 1]$ are step parameters. When $F: \mathbb{R}^n \mapsto \mathbb{R}^n$ is Lipschitz continuous and its Jacobian is negative definite, such an iterative scheme is known to converge to the root, if it exists (\citealp[][thm. 11.6]{nocedal2006}; \citealp[][prop. 1.2.4]{bertsekas1999}). A typical example occurs when using gradient ascent to maximize a strictly concave function whose gradient is $F$.

@@

\bibitem[Keane(1997)]{keane1997}
Keane, Michael P. 1997. ``Current Issues in Discrete Choice Modeling." \emph{Marketing Letters} 8(3): 307--22. {\url{http://www.jstor.org/stable/40216456}}.

>>>>

\subsection{Why the parameter update converges}
Consider the multivariate root-finding problem \[\text{find } \theta^*: F(\theta^*) = 0\]
and the iterative scheme \[\theta^{(t+1)} = \theta^{(t)} + \frac{\alpha}{t^r} F\left(\theta^{(t)} \right)\]
where $\alpha >0$ and $r \in (0, 1]$ are step parameters. When $F: \mathbb{R}^n \mapsto \mathbb{R}^n$ is Lipschitz continuous and its Jacobian is negative definite, such an iterative scheme is known to converge to the root, if it exists (\citealp[][prop. 1.2.4]{bertsekas1999}; \citealp[][thm. 11.6]{nocedal2006}). A typical example occurs when using gradient ascent to maximize a strictly concave function whose gradient is $F$.

@@

\bibitem[Keane(1997)]{keane1997}
Keane, Michael P. 1997. ``Current Issues in Discrete Choice Modeling." \emph{Marketing Letters} 8(3): 307--22. {\url{https://www.jstor.org/stable/40216456}}.
